---
title: "Homework 4"
author: "Brian Zhao"
date: "12/5/2020"
output:
  html_document:
    number_sections: false
    toc: true
    toc_float: 
      toc_collapsed: true
    toc_depth: 3
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup

## Libraries
```{r}
library("ggplot2")
library("dplyr")
library("gender")
library("geosphere")
library("ggmap")
library("lubridate")
```

## Import Data
```{r}
# airbnb <- read.csv("AB_NYC_2019.csv")
airbnb <- read.csv("AB_NYC_2019_Gender.csv")
```

## Explore Data
```{r}
str(airbnb)
head(airbnb)
tail(airbnb)
summary(airbnb)
```

## Clean Data
```{r, eval = FALSE}
# Create Gender Column (from Piazza)
airbnb$gender <- "unknown"
num <- 1
for (i in airbnb$host_name) {
  if (nrow(gender(i)['gender']) == 0) {
    airbnb$gender[num] <- "unknown"
  }
  else if (nrow(gender(i)['gender'] == 1) & gender(i)['gender'] == "male") {
    airbnb$gender[num] <- "male"
  }
  else if (nrow(gender(i)['gender'] == 1) & gender(i)['gender'] == "female") {
    airbnb$gender[num] <- "female"
  }
  num <- num + 1
}

airbnb$gender

# Write New Data File w/ Gender
write.csv(airbnb, "AB_NYC_2019_Gender.csv")
```

```{r}
# Create Description Length Column
airbnb$descLength <- nchar(airbnb$name, type = "chars", allowNA = FALSE, keepNA = NA)

# Create Keywords Column
airbnb$keyword <- "NA"
num <- 1
for (i in airbnb$name) {
  if ((grepl("cozy", i, fixed = TRUE)) || (grepl("Cozy", i, fixed = TRUE))) {
    airbnb$keyword[num] <- "Cozy"
  }
  else if ((grepl("large", i, fixed = TRUE)) || (grepl("Large", i, fixed = TRUE))) {
    airbnb$keyword[num] <- "Large"
  }
  else if ((grepl("cute", i, fixed = TRUE)) || (grepl("Cute", i, fixed = TRUE))) {
    airbnb$keyword[num] <- "Cute"
  }
  else if ((grepl("beautiful", i, fixed = TRUE)) || (grepl("Beautiful", i, fixed = TRUE))) {
    airbnb$keyword[num] <- "Beautiful"
  }
  else if ((grepl("!", i, fixed = TRUE))) {
    airbnb$keyword[num] <- "Exclaimation"
  }
  num <- num + 1
}

# Assign Factors
airbnb$neighbourhood_group <- as.factor(airbnb$neighbourhood_group)
airbnb$neighbourhood <- as.factor(airbnb$neighbourhood)
airbnb$room_type <- as.factor(airbnb$room_type)
airbnb$last_review <- as.Date(airbnb$last_review)
airbnb$gender <- as.factor(airbnb$gender)
airbnb$keyword <- as.factor(airbnb$keyword)
```

```{r}
str(airbnb)
```


# Questions

## 1. Calculate interesting metrics and build pursuasive visualizations that help us get a better understanding of the data. For example:
- Does gender of the Host affect the rental price?
```{r}
genderRates <- tapply(airbnb$price, airbnb$gender, mean, na.rm = TRUE)
barplot(sort(genderRates, decreasing = TRUE))
```

    It seems that on average rental prices are higher for hosts of "unknown" gender (which due to the gender function are often groups of people, such as couples or families). This is closely followed by male hosts, and it seems that female hosts command the lowest rental prices.

- How do rental rates differ between different boroughs
```{r}
neighbourhoodRates <- tapply(airbnb$price, airbnb$neighbourhood_group, mean, na.rm = TRUE)
barplot(sort(neighbourhoodRates, decreasing = TRUE))
```

    The most expensive listings are in Manhatten, and the least expensive listings are in the Bronx.

- Are reviews important?
```{r}
# Total Number of Reviews
ggplot(data = airbnb, aes(x = number_of_reviews, y = price)) + geom_smooth()
reviews_num_Rates <- tapply(airbnb$price, airbnb$number_of_reviews, mean, na.rm = TRUE)
barplot(reviews_num_Rates)
```

    Surprisingly, it seems that on average more total reviews leads to lower Airbnb rental prices. This could be caused by bad reviews. However, the most expensive Airbnb listings also tend be those with the most reviews. This leads me to believe that reviews are an indicator of the extremes, really good listings and really bad ones, while average ones are less reviewed.

```{r}
# Reviews per Month
ggplot(data = airbnb, aes(x = reviews_per_month, y = price)) + geom_smooth()
reviews_rpm_Rates <- tapply(airbnb$price, airbnb$reviews_per_month, mean, na.rm = TRUE)
barplot(reviews_rpm_Rates, ylim = c(0,1000))
```

    Reviews per month seems to follow a similar trend to total reviews at first with more reviews per month actually correlating to lower rental prices. However, at around 30 reviews per month this trend reverse and actually leads to slightly higher rental prices.

- Think of other questions that may be relevant and can be answered via exploration and visualization of this data.
```{r}
# SEE QUESTION 4
```


## 2. Use the latitude and longitude information to build map based visualizations that can provide further insights into the data. For example:
- Plot 100 most expensive rentals on the map. Do they show a geographic pattern?
```{r}
register_google(key = "AIzaSyDr6TG5wIRo6iXXvRbE0rV3n2EPx1jApRc", write = TRUE)

# Get Rental Info by Price
airbnb_stays <- airbnb %>%
  group_by(id) %>%
  summarise(lat = as.numeric(latitude),
            long = as.numeric(longitude),
            name = name,
            rental_price = price)

# Sort by Price
airbnb_stays <- airbnb_stays[order(airbnb_stays$rental_price, decreasing = TRUE),]

# Select 100 Most Expensive Rentals
airbnb_stays <- head(airbnb_stays, n = 100)

# Get Map and Plot Rental Locations
nyc_map <- get_map(location = 'New York City, New York', 
                       maptype ='roadmap', color='bw', source='google', zoom=11)

# Plot Map
ggmap(nyc_map) + 
  geom_point(data=airbnb_stays, aes(x=long, y=lat, color=rental_price), size=1, alpha=0.5) +
  scale_colour_gradient(high= "red", low= 'green') + 
  theme(axis.ticks = element_blank(), axis.text = element_blank()) +
  xlab('') + ylab('')
```

    It seems that the map reveals what we would expect based on our previous analyses. The most expensive rentals are as we expected primarily in Manhatten and some are in Brooklyn. Some patterns I recognized are that the most expensive listings seem to be clustered around geographical landmarks such as near Central Park or the water/beaches.


## 3. Does the description of the rental impact its price?
- Length of description?
```{r}
ggplot(data = airbnb, aes(x = descLength, y = price)) + geom_smooth()
```

    It seems that the optimal description length to charge the highest rental prices is around 100 characters. Longer and shorter descriptions generally command lower rental prices.

- Specific keywords?
```{r}
keywordRates <- tapply(airbnb$price, airbnb$keyword, mean, na.rm = TRUE)
barplot(sort(keywordRates, decreasing = TRUE))

```

    It seems that using the keyword "beautiful" and adding exclaimation marks in the description of the listing can lead to a higher rental price. Other popular keywords include "cozy," "cute," and "large," but these keywords seem to actually command a lower rental price than those without any of the keywords.


## 4. Any other interesting and insightful analysis that you may want to conduct.
- Is a entire (1) home/apt, (2) private room, (3) shared room cheaper?
```{r}
roomtypeRates <- tapply(airbnb$price, airbnb$room_type, mean, na.rm = TRUE)
barplot(roomtypeRates)
```

    Entire homes/apartments are much more expensive at an average of `r mean(airbnb[airbnb$room_type == "Entire home/apt", ]$price)` dollars compared to private rooms (`r mean(airbnb[airbnb$room_type == "Private room", ]$price)` dollars) and shared rooms (`r mean(airbnb[airbnb$room_type == "Shared room", ]$price)` dollars)

- What is the most common room type?
```{r}
# numEntire <- nrow(airbnb[airbnb$room_type == "Entire home/apt", ])
# numPrivate <- nrow(airbnb[airbnb$room_type == "Private room", ])
# numShared <- nrow(airbnb[airbnb$room_type == "Shared room", ])
ggplot(data = airbnb, aes(x=room_type)) + geom_bar()
```

    Most listings on Airbnb are for entire homes/apts

- What is the most common type of stay in each borough?
```{r}
ggplot(data = airbnb, aes(x=neighbourhood_group)) + geom_bar()
```

    Most listings are located in Manhattan and Brooklyn

- How does availability of a rental affect its price?
```{r}
ggplot(data = airbnb, aes(x = availability_365, y = price)) + geom_smooth()
availabilityRates <- tapply(airbnb$price, airbnb$availability_365, mean, na.rm = TRUE)
barplot(availabilityRates)
```

    As expect listings that are available for a larger percentage of the year are able to charge higher rental prices. However, there is a curious dip around 325/365 days a year. This could be because their lack of availablity is centered around holidays or popular travel times, where the Airbnb owner uses the property themselves instead of renting.

